\documentclass{beamer}
\usepackage[spanish]{babel}

\begin{document}


\begin{frame}
    \frametitle{plot} 

plot {graphics}	\hspace{5cm} R Documentation

\begin{center}
Generic X-Y Plotting
\end{center}

{\footnotesize

\textbf{Description}

\vspace{2mm}

Generic function for plotting of R objects. For more details about the graphical parameter arguments, see {\color{blue} par}.

For simple scatter plots, {\color{blue} plot.default} will be used. However, there are plot methods for many R objects, including {\color{blue} function}S, {\color{blue}data.frame}S, {\color{blue} density} objects, etc. Use methods(plot) and the documentation for these.

\vspace{2mm} 

\textbf{Usage}

plot(x, y, ...)

}

\end{frame}


\begin{frame}
    \frametitle{plot} 

{\footnotesize

\textbf{Arguments}

\textbf{x} - 
the coordinates of points in the plot. Alternatively, a single plotting structure, function or any R object with a plot method can be provided.

\textbf{y} - 
the y coordinates of points in the plot, optional if x is an appropriate structure.

\textbf{...}-
Arguments to be passed to methods, such as graphical parameters (see par). Many methods will accept the following arguments:

}



\end{frame}


\begin{frame}
    \frametitle{plot} 
 
 {\footnotesize
   
\textbf{type} -
what type of plot should be drawn. Possible types are

\begin{itemize}
\item  "p" for points,
\item "l" for lines,
\item "b" for both,
\item "c" for the lines part alone of "b",
\item "o" for both ‘overplotted’,
\item "h" for ‘histogram’ like (or ‘high-density’) vertical lines,
\item "s" for stair steps,
\item "S" for other steps, see ‘Details’ below,
\item "n" for no plotting.
\end{itemize}
 }
 
 
 \end{frame} 


\begin{frame}
    \frametitle{plot} 
 
 {\footnotesize
 
\textbf{main} -
an overall title for the plot: see title.

\textbf{sub} -
a sub title for the plot: see title.

\textbf{xlab} -
a title for the x axis: see title.

\textbf{ylab} -
a title for the y axis: see title.

 }
 
 
 \end{frame} 
 
 \begin{frame}
    \frametitle{plot} 
 
 {\footnotesize

\textbf{Details}

The two step types differ in their x-y preference: Going from (x1,y1) to (x2,y2) with x1 $<$ x2, type = "s" moves first horizontal, then vertical, whereas type = "S" moves the other way around.

\vspace{2mm}

\textbf{See Also}

{\color{blue} plot.default, plot.formula} and other methods; {\color{blue}points, lines, par}. For thousands of points, consider using {\color{blue}smoothScatter()} instead of plot().

For X-Y-Z plotting see {\color{blue}contour, persp} and {image}.

 }
 
 \end{frame} 


 \begin{frame}
    \frametitle{plot} 
 
 {\footnotesize

\textbf{Examples}

\vspace{2mm}

require(stats) \# for lowess, rpois, rnorm

plot(cars)

lines(lowess(cars))

\vspace{2mm}

plot(sin, -pi, 2*pi) \# see ?plot.function

\vspace{2mm}

\#\# Discrete Distribution Plot:

plot(table(rpois(100, 5)), type = "h", col = "red", lwd = 10,

     main = "rpois(100, lambda = 5)")

\vspace{2mm}

\#\# Simple quantiles/ECDF, see ecdf() {library(stats)} for a better one:

plot(x <- sort(rnorm(47)), type = "s", main = "plot(x, type = \"s\")")

points(x, cex = .5, col = "dark red")
}
 
 \end{frame} 

\end{document}